\section{Background}

% Build up...
In conjunction with increasing performance, memory and storage on modern computers, the capacity for large amounts of varied content in games, movies, and other digital media grows respectively.
However, content creators' capabilities to fully utilize this potential by hand, remains a slow and expensive process.
Because of this, many companies have decided to leverage the use of algorithms in order to create large amounts of rich and varied content.
These algorithms are part of an exciting field within computer science called Procedural Content Generation (PCG).

% What is PCG? (definition)
PCG is a family of algorithms where content such as environments, textures, stories, items, quests, music, weapons, etc.\ is randomly generated rather than designed by hand~\cite[p.1]{PCG_in_games}.
Typically, this is achieved by combining assets and algorithms with computer-generated randomness to synthesize unique content.
However calling it completely random would be incorrect.
The algorithm takes advantage of randomness within its manually defined constraints to generate desired content~\cite{Gamasutra}.
For instance, a PCG algorithm for terrain generation would not construct unreasonable terrain such as lakes flying in the air or trees growing upside down (unless this is intentional).
	
% History and significance
In the early 1980s, PCG was primarily used in games as a work-around for the limited storage space~\cite[p.4]{PCG_in_games}.
In recent years however, the technique has gained a lot of attraction in modern games for generating compelling and replayable experiences.
Games such as Diablo~\cite{diablo} feature procedural generation for the creation of the maps and as well as the placement and number of items and monsters~\cite[p.4]{PCG_in_games}.
In Spore~\cite{spore}~, the animation of the creature the player designs use procedural animation techniques\cite[p.4]{PCG_in_games}.
Furthermore, the popular game Minecraft~\cite{minecraft} make use of PCG techniques extensively for generating everything from the cave-systems to the mountains to the whole world~\cite[p.4]{PCG_in_games}.
Procedural generation can be used to generate pretty much any virtual content you could imagine.
Evident from the use of PCG in big commercial games there is a demand from the game industry to create large, impressive and unique environments for their player base to explore.

% More specific games


\input{tex/introduction/theory.tex}
\input{tex/introduction/related_works.tex}

% Benefits
% A key question to consider is what the actual benefits are of using PCG over manual design is.
% With the help of PCG, software can produce impressive, varied and seemingly endless environments order of magnitudes faster than a human~\cite[p.3]{PCG_in_games}.
% This aids designers to create a lot more content cheaply and efficiently once the algorithm has been developed.
% Additionally, as soon as the algorithm is done it can be reused. Similar to a debugger, a PCG algorithm can be infinitely run afterwards. The algorithm can potentially be reused to generate completely different content from.

% Although the output space of PCG is considerable, automatic content generation comes with a set of obstacles.
% One of the challenges when developing PCG systems is the ability to generate content comparable with the quality of hand-crafted content.
% In the case of hand-crafted content, the content would undoubtedly fit its intended use case whereas generated content might be deemed inadequate or specific enough.
% This difficulty also ties into the problem of generating visually distinctive and expressive content.
% If the generated content only differs with minimal variance it might not actually be perceived as varied content at all as
% the computed creativity PCG offers has its limits. For instance, there are no reasonable automatic novel creators. Kate Compton, who is a programmer that worked on Spore's and SimCity's content generation, had a presentation about the utilities that PCG offers. She mentions that writing a novel is too general of a task for PCG to generate, and that PCG excells to generate very specifically defined~\cite{PCG_for_everyone}. Although it is technically possible it would not compare well to human novel writing.