\chapter{Introduction}

% Why was the study undertaken i.e. why was this paper written?
% Proper acknowledgements of previous works
% Focus on thesis question(s)
% All cited sources should be directly relevant to the goals of the thesis
% Explain the scope. What will and what will not be included.
% Verbal road map of what's ahead
% Where do old work end and where do our work begin?


% The problem PCG solves.
In conjunction with increasing performance, memory and storage available on modern computers, the capacity for large amounts of varied content in games, movies, and other digital media grows respectively.
However, the capability to manually produce interesting content that can fully utilize this potential remains a slow and expensive process.
Consequently, many companies have decided to leverage the use of algorithms to partly, and sometimes completely, automate the production of such digital content.
These algorithms are part of an exciting research field within computer science called Procedural Content Generation (PCG).

This thesis explores the usage of such PCG algorithms in order to find a suitable approach for procedural generation of modern 3D cities.
The investigation is conducted through the development of a user-friendly desktop application that can interactively generate and export models of 3D cities.
These models can then be used in third-party modeling software and game engines.
Thus, with this report we contribute with insight into various techniques applicable to city generation, as well as an open-source, MIT licensed application called \textit{CityCraft} that demonstrates such generation.

This chapter introduces the project, its goals, and some related works that have been previously done in the field of city generation.
Thereafter, follows a background chapter about the applications of PCG, and a theory chapter covering many of the fundamental techniques considered.
Finally, the project's methods and results are presented, followed up by a discussion chapter and some notes for future work.

\newpage

% Why?
\input{tex/introduction/purpose.tex}
% What and what not? I.e., what exactly?
\input{tex/introduction/goal.tex}
% Is this reasonable?
\input{tex/introduction/ethics.tex}
% What have others done?
\input{tex/introduction/related_works.tex}